Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Add raw time series figure for social cohesion

```{r tweet-count, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

@@

@@

#### Metrics
For WCRQA analyses, we decided to focus on RR and DET.

>>>>

@@

The raw social cohesion time series can be seen in Figure \@ref(fig:raw-cohesion).

```{r raw-cohesion-ts, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="Raw social cohesion metric time series."}

# plot time series
raw_cohesion_ts <- ggplot(cohesion_df, aes(x= as.Date(Date), y=MeanCohesion)) +
  geom_point() +
  geom_line() +
  xlab("Date") +
  ylab("Mean Social Cohesion")
ggsave("./results/primary/raw-cohesion-ts.png")

# call the image
knitr::include_graphics("./results/primary/raw-cohesion-ts.png")

@@

#### Metrics
For WCRQA analyses, we decided to focus on RR and DET, but WCRQA visualization can be done for any metric desired.
